\documentclass[letterpaper,10pt]{extarticle}
\usepackage[letterpaper, margin=0.5in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[table,xcdraw]{xcolor}
\usepackage{hhline}
\usepackage{verse}
\setlength\tabcolsep{0pt}
\newcommand{\puzzlesize}[1]{{\fontsize{14.4pt}{0.1em}\selectfont #1}}
\newcommand{\hdash}{{\fontsize{30pt}{0.1em}\selectfont \_}}
\newcommand{\pzsp}{{\fontsize{24.88pt}{0.1em}\selectfont \phantom{I}}}
\newcolumntype{G}{>{\columncolor[gray]{0.9}}c}
\begin{document}
\begin{center}
   \Large\textbf{Vograbulary}\\
   \large\textit{by Don Kirkby}
\end{center}
{\fontsize{10pt}{0.1em}\selectfont
There are two kinds of puzzles in this collection. Solutions are listed at the
end.

\textbf{Sorted Poetry} - each puzzle starts with a poem, then the letters in
each word are sorted. To solve the puzzle, find the original words and read the
poem.

If you get stuck on the last few words, there is a clue section at the bottom of
each poem. It shows the letters that appear in each column, so cross out the
letters you've already solved to see a letter from the unsolved word in that
column.

\textbf{Russian Dolls} - based on an episode of the radio show Ask Me Another.
Each puzzle gives a clue with two words highlighted. One of those words gets put
completely inside the other to make the solution word. The letters in each word
don't get rearranged, one complete word gets nested inside the other like two
Russian dolls. Here's an example puzzle:

When you are *unable* to find *comfort*.

The two words are "unable" and "comfort", and "comfort" nests inside "unable" to
form "uncomfortable".
}

## insert-puzzles ##
\end{document}